### 2020-08-15 ChapterBackground/chapterBackground.tex
Fixed: Minor fixes to background

Although there has been research utilising multiple servers to distribute the task of solving physics based problems (e.g., \cite{mashayekhi2018automatically}), there is no known literature describing real-time interactive physics exploiting the addition of servers to gain scalability. The closest work to this challenge is that carried out to seek scalability in terms of player numbers in online gaming in the field of Distributed Virtual Environments (DVEs).

Online gaming is a subset of DVEs and so many principles that apply to DVEs also apply to online gaming. Some key aspects to consider are the Goals and requirements of real-time DVEs are different from other distributed simulations. DVEs only need be "sufficiently realistic", which differs depending on context. This is known as selective fidelity, where different levels of realism are applied selectively to different aspects of the simulation, depending upon how much the aspect affects the outcome of the simulation. For example, in a ship simulator, realistic looking clouds will not contribute to simulator's effectiveness as a training device. DVEs must execute in real-time, unlike non-real-time simulations. Repeatability and synchronisation requirements are often relaxed as they may not contribute to the overall goal of the DVE, whereas they are essential for non-real-time simulations that require a high degree of accuracy. As a result of these different goals and requirements, many of the algorithms and techniques used in non-real-time simulations are not suitable for use in real-time DVEs \cite{fujimoto2000parallel}.

@@

\subsection{Distributed Virtual Environments - Summary}
In the case of real-time physics, we can assume the use of either homogeneous simulations or at least simulations that will be simulating physics with a large degree of shared semantics between simulations (as all simulations are dealing with physical simulation). As a result of this, there is little to no advantage gained in using the HLA architecture or similar and direct communication between servers has the benefit of lower latency between servers.

>>>>

Although there has been research utilising multiple servers to distribute the task of solving physics based problems (e.g., \cite{mashayekhi2018automatically}), there is no known literature describing real-time interactive physics exploiting the addition of servers to gain scalability. The closest work to this challenge is that carried out to seek scalability in terms of player numbers in online gaming in the field of Distributed Virtual Environments (DVEs), of which online gaming can be considered a subcategory.

Some key aspects to consider are the Goals and requirements of real-time DVEs, which are different from other distributed simulations. DVEs only need be "sufficiently realistic", which differs depending on context. This is known as selective fidelity, where different levels of realism are applied selectively to different aspects of the simulation, depending upon how much the aspect affects the outcome of the simulation. For example, in a ship simulator, realistic looking clouds will not contribute to simulator's effectiveness as a training device. DVEs must execute in real-time, unlike non-real-time simulations. Repeatability and synchronisation requirements are often relaxed as they may not contribute to the overall goal of the DVE, whereas they are essential for non-real-time simulations that require a high degree of accuracy. As a result of these different goals and requirements, many of the algorithms and techniques used in non-real-time simulations are not suitable for use in real-time DVEs \cite{fujimoto2000parallel}.

@@

In the case of real-time physics, we can assume the use of either homogeneous simulations or at least simulations that will be simulating physics with a large degree of shared semantics between simulations (as all simulations are dealing with physical simulation). As a result of this, there is little to no advantage gained in using the HLA architecture or similar and direct communication between servers has the benefit of lower latency between servers.
